Glasgow Hackerspace CIC Articles of Association

### 2024-03-01 articles.tex
Commit changes from Overleaf, for final submission

\documentclass[12pt]{article}
%\usepackage[scaled]{helvet}
%\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage[a4paper, margin=0.5in]{geometry}
% \usepackage{graphicx} % Required for inserting images
\usepackage{hang}
% \usepackage{endnotes}
\usepackage[indentafter]{titlesec}
\usepackage[singlespacing]{setspace}
\usepackage{changepage}
% Colourisation of certain clauses
%'
%' As regards to colour (like red text in the template we used),
%' use the \textcolor command directly on the block of text which is to
%' be coloured, not, e.g. wrapping a whole \itemize list or wrapping a
%' \subsection{} list.
%'
%' The reason for this is that the section numbering looks odd,
%' and for some reason it also introduces a spurrious new-line before the
%' list or section. It also seems to affect the indentation, even though
%' the only thing which changes is the colour.
\usepackage{xcolor}

@@

% Custom section formatting
%'
%' This compliments the section numbering above: note no argument
%' \thesection in \section*'s \titleformat incantation.
%'
%' The hang part in sub-/sub-sub-sections is pretty important.
%' The text otherwise appears at the very start of the next line!
%' I don't know why block doesn't work like this.
%' I just tried each titlesec shape option in the manual until I found
%' this one worked best.
%'
%' The desired behaviour of indentation of subsequent text is actually in
%' conflict with the expected behaviour. The expected behaviour is that
%' subsequent text should be aligned with the section body, which it is,
%' as our sub-/sub-sub-sections are not indented.
%'
%' Actually getting it to be aligned with the section body was fairly
%' difficult. One trick which works is to have the section body be a
%' text-box with a predictable indentation from the line, and also to
%' align the box to the left.
%'
%' I have defined a variable \clauseident which is inherited by the
%' sub/sub-sub-sections' as well as the \hangindent. I think it looks
%' good if those are roughly the same size.
%'
%' The neat suggestion to use a text box was adapted from the following TeX StackExchange answer: https://tex.stackexchange.com/questions/405372/align-section-with-text-body/405373#405373
%'
\def\clauseindent{30pt}

\titleformat{\section}[runin]% Section to customise
            {\Large\bfseries}% Title text format
            {}%                Title body
            {0pt}%             Horizontal separation between label/title body
            {}%                Space before title body
            []%                Space after title body
\titleformat{\subsection}[hang]{\bfseries}{\makebox[\clauseindent][l]{\thesubsection.}}{0pt}{}
\titleformat{\subsubsection}[hang]{\mdseries}{\makebox[\clauseindent][l]{\thesubsubsection.}}{0pt}{}

@@

% Environment to set indentation + hanging paragraph on lists
%' This is from the hang package, whereas the similarly-named hanging
%' package doesn't support itemised lists.
%'
% There are actually two types of indentation:
%' 1. A series of hanging paragraphs in a list (these are not labelled (a), (b) &c.)
%' 2. Indented lists, which aren't hanging (these are labelled (a), (b) &c.)
%'
%' The hang package actually supports both. I thought it was odd that it
%' didn't have labelled hanging lists, but I see in the template that they
%' don't hang labelled list items!
%'
\setlength{\hangingindent}{\clauseindent}
\newenvironment{subindentpara}{\begin{adjustwidth}{\clauseindent}{}\begin{hanginglist}}{\end{hanginglist}\end{adjustwidth}}
\newenvironment{subindentlist}{\begin{adjustwidth}{\clauseindent}{}\begin{labeledlist}{\clauseindent}}{\end{labeledlist}\end{adjustwidth}}

@@

@@

\begin{document}
\renewcommand\contentsname{
    \bfseries\Large{Index to the Articles}\newline
}
% \maketitle % todo: add CIC etc
\tableofcontents

\section*{Interpretation}
\addcontentsline{toc}{section}{Interpretation}

@@

\section*{Community Interest Company and Asset Lock}
\addcontentsline{toc}{section}{Community Interest Company and Asset Lock}

% The following sub-section is highlighted in red in template: Obviously fundamental to C.I.C. operation!
\subsection{Community Interest Company}
\subsubsection[Community Interest Company]{\textcolor{red}{The Company is to be a community interest company.}}
% The following sub-section is highlighted in red in template: Fundamental to C.I.C. operation!
\subsection{Asset Lock}
  \subsubsection[Full Consideration of Assets]{\textcolor{red}{The Company shall not transfer any of its assets other than for full consideration.}}\label{subsubsubsection:fullconsideration}
  \subsubsection[Specifics of Full Consideration of Assets]{\textcolor{red}{Provided the conditions in \fancyref{subsubsection:metaassetrestr} are satisfied, \fancyref{subsubsubsection:fullconsideration} shall not apply to:}}\label{subsubsection:transferrestrictions}
  \begin{subindentlist}
    \item [(a)] \textcolor{red}{the transfer of assets to any specified asset-locked body, or (with the consent of the Regulator) to any other asset-locked body; and}
    \item [(b)] \textcolor{red}{The conditions are that the transfer of assets must comply with any restrictions on the transfer of assets for less than full consideration which may be set out elsewhere in the Memorandum and Articles of the Company.}
  \end{subindentlist}
  \subsubsection[Conditions of transfer of assests]{The conditions are that the transfer of assets must comply with any restrictions on the transfer of assets for less than full consideration which may be set out elsewhere in the Memorandum and Articles of the Company.}\label{subsubsection:metaassetrestr}
% The following sub-section is not highlighted in red, but don't remove this, as it's fundamental to the space's model!
\subsection{Not For Profit}
\subsubsection[Investiture of assets or surplus in community]{The Company is not established or conducted for private gain: any surplus or assets are
used principally for the benefit of the community.}

\section*{Objects, Powers and Limitation of Liability}
\addcontentsline{toc}{section}{Objects, Powers and Limitation of Liability}

@@

\section*{Directors}
\addcontentsline{toc}{section}{Directors}
\section*{Directors' Powers and Responsibilities}
\addcontentsline{toc}{section}{Directors' Powers and Responsibility}

@@

\subsection{Treasurer}
\subsubsection{One of the Directors shall be the treasurer.}
\subsubsection[Automatic termination of Treasurer]{A person elected to be treasurer shall automatically cease to hold that office:}
\begin{subindentlist}
  \item if they cease to be a Director; or
  \item if they give to the Hackerspace a notice of resignation from that office, signed by them.
\end{subindentlist}
\subsubsection[Replacement treasurer must be appointed]{If the treasurer ceases to hold that office, or the office of Director, the remaining Directors shall appoint a replacement treasurer from amongst their number.}

@@

\section*{Decision-Making by Directors}
\addcontentsline{toc}{section}{Decision-Making by Directors}

@@

% The following sub-section is highlighted in red in template:
\subsection{Decision making at a meeting}
  \subsubsection[Majority voting at a Directors' meeting]{\textcolor{red}{Questions arising at a Directors' meeting shall be decided by a majority of votes.}}
  \subsubsection[A given Director has only one vote at a Director's meeting]{\textcolor{red}{In all proceedings of Directors each Director must not have more than one vote.}}
\subsection{Decisions without a meeting}\label{subsubsection:withoutmeeting}
\subsubsection[Directors' unanimous decisions by other means]{The Directors may take a unanimous decision without a Directors' meeting by indicating to each other by any means, including without limitation by Electronic Means, that they share a common view on a matter. Such a decision may, but need not, take the form of a resolution in Writing, copies of which have been signed by each Director or to which each Director has otherwise indicated agreement in Writing.}\label{subsubsubsection:unanimous}

@@

\section*{Appointment and Retirement of Directors}
\addcontentsline{toc}{section}{Appointment and Retirement of Directors}

@@

\section*{Members}
\addcontentsline{toc}{section}{Members}
\section*{Becoming and Ceasing to be a Member}
\addcontentsline{toc}{section}{Becoming and Ceasing to be a Member}

@@

\subsection{Becoming a member}
\subsubsection[First Members of the Company]{\textcolor{red}{The subscribers to the Memorandum are the first Members of the Company.}}
\subsubsection[Members are admitted in accordance with Articles]{\textcolor{red}{Such other persons as are admitted to membership in accordance with the Articles shall be Members of the Company.}}
\subsubsection[Potential Members must be approved by Directors]{\textcolor{red}{No person shall be admitted a member of the Company unless they are approved by the Directors.}}
\subsubsection[Potential Members must apply for membership]{\textcolor{red}{Every person who wishes to become a Member shall deliver to the Company an application for membership in such form (and containing such information) as the Directors require and executed by the Member.}} % todo is this executed by the member? this was him or her before
\subsubsection[Directors must notify potential Members of a decision]{The Directors must notify each applicant for membership promptly (in Writing, including by Electronic Means) of its decision on whether or not to admit them to membership.} % Not red in original document
\subsubsection[Members may not be organisations]{Members must be a physical person. Organisations are not eligible for membership.} % Not red in template

@@

\subsection{Termination of membership}
\subsubsection{Membership is not transferable to anyone else.}
\subsubsection[Specifics of termination of membership]{Membership is terminated if:}
\begin{subindentpara}
    \item \textcolor{red}{the Member dies or ceases to exist;}
    \item \textcolor{red}{otherwise in accordance with the Articles;}
    \item the Member fails to pay the membership subscription for more than 3 months, and has not been granted an exemption by the Directors;
    \item the Member notifies the Hackerspace, via any means on which a director may be reached (in writing, including by Electronic Means) that they wish to cease to be a member; in which case, the Member ceases to be a Member from the time when the notice is received;
    \item the Member is expelled by way of a resolution passed by not less than two thirds of those present and voting at a general meeting, providing the following procedures have been observed: 
    \begin{subindentpara} % Note initial indentation of this child indented paragraph section may go too far. Largely unimportant, but note it inherits absolute indentation of regular hanging paragraphs from the margin.
        \item at least 21 days notice of the intention to propose the resolution must be given to the Member concerned,  specifying the grounds for the proposed expulsion; or
        \item the Member concerned will be entitled to be heard on the resolution at the general meeting at which the resolution is proposed
    \end{subindentpara}
    \item or;
    \item the Directors may temporarily suspend any Member from access to the Hackerspace's resources, if the behaviour of that Member is deemed by the Directors to be unacceptable to the Hackerspace. Suspension will continue until either the Directors reverse the suspension, or an expulsion resolution is heard. The suspended Member has the right to propose an expulsion resolution. A Member expelled by such a resolution will nevertheless remain liable to pay to the Company any subscription or other sum owed by that Member.
\end{subindentpara}
\subsubsection[Return of keys upon membership termination]{Upon ceasing to be a Member, all means of access to the Hackerspace, including but not limited to keys and access tokens, must be returned to the Hackerspace.}

\section*{Organisation of General Meetings}
\addcontentsline{toc}{section}{Organisation of General Meetings}

@@

\section*{Voting at General Meetings}
\addcontentsline{toc}{section}{Voting at General Meetings}

\subsection{General}
\subsubsection{A resolution put to the vote of a general meeting must be decided on a show of hands unless a poll is duly demanded in accordance with the Articles.}
\subsubsection[Only Members may vote at general meetings]{\textcolor{red}{A person who is not a member of the Company shall not have any right to vote at a general meeting of the Company; but this is without prejudice to any right to vote on a resolution affecting the rights attached to a class of the Company's debentures.}} \label{subsubsection:nonmemberVoting}
\subsubsection[Proxies may vote on Members' behalf]{\fancyref{subsubsection:nonmemberVoting} shall not prevent a person who is a proxy for a member from voting at a general meeting of the Company.}

@@

\section*{Written Resolutions}
\addcontentsline{toc}{section}{Written Resolutions}

@@

\section*{Administrative Arrangements and Miscellaneous}
\addcontentsline{toc}{section}{Administrative Arrangements and Miscellaneous}

>>>>

\documentclass[12pt]{article}
%\usepackage[scaled]{helvet}
%\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage[a4paper, margin=0.5in]{geometry}
% \usepackage{graphicx} % Required for inserting images
\usepackage{hang}
% \usepackage{endnotes}
\usepackage[indentafter]{titlesec}
\usepackage[singlespacing]{setspace}
\usepackage{changepage}
\usepackage{ragged2e}
% Colourisation of certain clauses
%'
%' As regards to colour (like red text in the template we used),
%' use the \textcolor command directly on the block of text which is to
%' be coloured, not, e.g. wrapping a whole \itemize list or wrapping a
%' \subsection{} list.
%'
%' The reason for this is that the section numbering looks odd,
%' and for some reason it also introduces a spurrious new-line before the
%' list or section. It also seems to affect the indentation, even though
%' the only thing which changes is the colour.
\usepackage{xcolor}

@@

% Custom section formatting
%'
%' This compliments the section numbering above: note no argument
%' \thesection in \section*'s \titleformat incantation.
%'
%' The hang part in sub-/sub-sub-sections is pretty important.
%' The text otherwise appears at the very start of the next line!
%' I don't know why block doesn't work like this.
%' I just tried each titlesec shape option in the manual until I found
%' this one worked best.
%'
%' The desired behaviour of indentation of subsequent text is actually in
%' conflict with the expected behaviour. The expected behaviour is that
%' subsequent text should be aligned with the section body, which it is,
%' as our sub-/sub-sub-sections are not indented.
%'
%' Actually getting it to be aligned with the section body was fairly
%' difficult. One trick which works is to have the section body be a
%' text-box with a predictable indentation from the line, and also to
%' align the box to the left.
%'
%' I have defined a variable \clauseident which is inherited by the
%' sub/sub-sub-sections' as well as the \hangindent. I think it looks
%' good if those are roughly the same size.
%'
%' The neat suggestion to use a text box was adapted from the following TeX StackExchange answer: https://tex.stackexchange.com/questions/405372/align-section-with-text-body/405373#405373
%'
\def\clauseindent{30pt}
\def\fakecolour{black}

\titleformat{\section}[runin]% Section to customise
            {\Large\bfseries}% Title text format
            {}%                Title body
            {0pt}%             Horizontal separation between label/title body
            {}%                Space before title body
            []%                Space after title body
\titleformat{\subsection}[hang]{\raggedright\bfseries}{\makebox[\clauseindent][l]{\thesubsection.}}{0pt}{}
\titleformat{\subsubsection}[hang]{\raggedright\mdseries}{\makebox[\clauseindent][l]{\thesubsubsection.}}{0pt}{}

@@

% Environment to set indentation + hanging paragraph on lists
%' This is from the hang package, whereas the similarly-named hanging
%' package doesn't support itemised lists.
%'
% There are actually two types of indentation:
%' 1. A series of hanging paragraphs in a list (these are not labelled (a), (b) &c.)
%' 2. Indented lists, which aren't hanging (these are labelled (a), (b) &c.)
%'
%' The hang package actually supports both. I thought it was odd that it
%' didn't have labelled hanging lists, but I see in the template that they
%' don't hang labelled list items!
%'
\setlength{\hangingindent}{\clauseindent}
\newenvironment{subindentpara}{\raggedright\begin{adjustwidth}{\clauseindent}{}\begin{hanginglist}}{\end{hanginglist}\end{adjustwidth}}
\newenvironment{subindentlist}{\raggedright\begin{adjustwidth}{\clauseindent}{}\begin{labeledlist}{\clauseindent}}{\end{labeledlist}\end{adjustwidth}}

@@

\usepackage{titling}
\renewcommand\maketitlehooka{\null\mbox{}\vfill}
\renewcommand\maketitlehookd{\vfill\null}

@@

\begin{document}
\renewcommand\contentsname{
    \centering\bfseries\Large{Index to the Articles}\newline\justifying
}

\maketitle
\newpage
\tableofcontents
\newpage

\vspace{1.5\baselineskip}\section*{Interpretation}
\addcontentsline{toc}{section}{Interpretation}

@@

\vspace{1.5\baselineskip}\section*{Community Interest Company and Asset Lock}
\addcontentsline{toc}{section}{Community Interest Company and Asset Lock}

% The following sub-section is highlighted in red in template: Obviously fundamental to C.I.C. operation!
\subsection{Community Interest Company}
\subsubsection[Community Interest Company]{\textcolor{\fakecolour}{The Company is to be a community interest company.}}
% The following sub-section is highlighted in red in template: Fundamental to C.I.C. operation!
\subsection{Asset Lock}
  \subsubsection[Full Consideration of Assets]{\textcolor{\fakecolour}{The Company shall not transfer any of its assets other than for full consideration.}}\label{subsubsubsection:fullconsideration}
  \subsubsection[Specifics of Full Consideration of Assets]{\textcolor{\fakecolour}{Provided the conditions in \fancyref{subsubsection:metaassetrestr} are satisfied, \fancyref{subsubsubsection:fullconsideration} shall not apply to:}}\label{subsubsection:transferrestrictions}
  \begin{subindentlist}
    \item [(a)] \textcolor{\fakecolour}{the transfer of assets to any specified asset-locked body, or (with the consent of the Regulator) to any other asset-locked body; and}
    \item [(b)] \textcolor{\fakecolour}{The conditions are that the transfer of assets must comply with any restrictions on the transfer of assets for less than full consideration which may be set out elsewhere in the Memorandum and Articles of the Company.}
  \end{subindentlist}
  \subsubsection[Conditions of transfer of assests]{The conditions are that the transfer of assets must comply with any restrictions on the transfer of assets for less than full consideration which may be set out elsewhere in the Memorandum and Articles of the Company.}\label{subsubsection:metaassetrestr}
% The following sub-section is not highlighted in red, but don't remove this, as it's fundamental to the space's model!
\subsection{Not For Profit}
\subsubsection[Investiture of assets or surplus in community]{The Company is not established or conducted for private gain: any surplus or assets are
used principally for the benefit of the community.}

% New page is here because for some reason, Objects, Powers &c. has a
% new page afterwards, despite not setting one.
% Instead, manually set one before it, which conveniently moves it down
% to the text below.
\vspace{1.5\baselineskip}\newpage\section*{Objects, Powers and Limitation of Liability}
\addcontentsline{toc}{section}{Objects, Powers and Limitation of Liability}

@@

\newpage\section*{Directors}
\addcontentsline{toc}{section}{Directors}
\vspace{1.5\baselineskip}\section*{Directors' Powers and Responsibilities}
\addcontentsline{toc}{section}{Directors' Powers and Responsibility}

@@

\subsection{Treasurer}
\subsubsection{One of the Directors shall be the treasurer.}
\subsubsection[Automatic termination of Treasurer]{A person elected to be treasurer shall automatically cease to hold that office:}
\begin{subindentlist}
  \item [(a)] if they cease to be a Director; or
  \item [(b)] if they give to the Hackerspace a notice of resignation from that office, signed by them.
\end{subindentlist}
\subsubsection[Replacement treasurer must be appointed]{If the treasurer ceases to hold that office, or the office of Director, the remaining Directors shall appoint a replacement treasurer from amongst their number.}

@@

\vspace{1.5\baselineskip}\section*{Decision-Making by Directors}
\addcontentsline{toc}{section}{Decision-Making by Directors}

@@

% The following sub-section is highlighted in red in template:
\subsection{Decision making at a meeting}
  \subsubsection[Majority voting at a Directors' meeting]{\textcolor{\fakecolour}{Questions arising at a Directors' meeting shall be decided by a majority of votes.}}
  \subsubsection[A given Director has only one vote at a Director's meeting]{\textcolor{\fakecolour}{In all proceedings of Directors each Director must not have more than one vote.}}
\subsection{Decisions without a meeting}\label{subsubsection:withoutmeeting}
\subsubsection[Directors' unanimous decisions by other means]{The Directors may take a unanimous decision without a Directors' meeting by indicating to each other by any means, including without limitation by Electronic Means, that they share a common view on a matter. Such a decision may, but need not, take the form of a resolution in Writing, copies of which have been signed by each Director or to which each Director has otherwise indicated agreement in Writing.}\label{subsubsubsection:unanimous}

@@

\newpage\section*{Appointment and Retirement of Directors}
\addcontentsline{toc}{section}{Appointment and Retirement of Directors}

@@

\newpage\section*{Members}
\addcontentsline{toc}{section}{Members}
\vspace{1.5\baselineskip}\section*{Becoming and Ceasing to be a Member}
\addcontentsline{toc}{section}{Becoming and Ceasing to be a Member}

@@

\subsection{Becoming a member}
\subsubsection[First Members of the Company]{\textcolor{\fakecolour}{The subscribers to the Memorandum are the first Members of the Company.}}
\subsubsection[Members are admitted in accordance with Articles]{\textcolor{\fakecolour}{Such other persons as are admitted to membership in accordance with the Articles shall be Members of the Company.}}
\subsubsection[Potential Members must be approved by Directors]{\textcolor{\fakecolour}{No person shall be admitted a member of the Company unless they are approved by the Directors.}}
\subsubsection[Potential Members must apply for membership]{\textcolor{\fakecolour}{Every person who wishes to become a Member shall deliver to the Company an application for membership in such form (and containing such information) as the Directors require and executed by the Member.}} % todo is this executed by the member? this was him or her before
\subsubsection[Directors must notify potential Members of a decision]{The Directors must notify each applicant for membership promptly (in Writing, including by Electronic Means) of its decision on whether or not to admit them to membership.} % Not red in original document
\subsubsection[Members may not be organisations]{Members must be a physical person. Organisations are not eligible for membership.} % Not red in template

@@

\subsection{Termination of membership}
\subsubsection{Membership is not transferable to anyone else.}
\subsubsection[Specifics of termination of membership]{Membership is terminated if:}
\begin{subindentpara}
    \item \textcolor{\fakecolour}{the Member dies or ceases to exist;}
    \item \textcolor{\fakecolour}{otherwise in accordance with the Articles;}
    \item the Member fails to pay the membership subscription for more than 3 months, and has not been granted an exemption by the Directors;
    \item the Member notifies the Hackerspace, via any means on which a director may be reached (in writing, including by Electronic Means) that they wish to cease to be a member; in which case, the Member ceases to be a Member from the time when the notice is received;
    \item the Member is expelled by way of a resolution passed by not less than two thirds of those present and voting at a general meeting, providing the following procedures have been observed: 
    \begin{subindentpara} % Note initial indentation of this child indented paragraph section may go too far. Largely unimportant, but note it inherits absolute indentation of regular hanging paragraphs from the margin.
        \item at least 21 days notice of the intention to propose the resolution must be given to the Member concerned,  specifying the grounds for the proposed expulsion; or
        \item the Member concerned will be entitled to be heard on the resolution at the general meeting at which the resolution is proposed
    \end{subindentpara}
    \item or;
    \item the Directors may temporarily suspend any Member from access to the Hackerspace's resources, if the behaviour of that Member is deemed by the Directors to be unacceptable to the Hackerspace. Suspension will continue until either the Directors reverse the suspension, or an expulsion resolution is heard. The suspended Member has the right to propose an expulsion resolution. A Member expelled by such a resolution will nevertheless remain liable to pay to the Company any subscription or other sum owed by that Member.
\end{subindentpara}
\subsubsection[Return of keys upon membership termination]{Upon ceasing to be a Member, all means of access to the Hackerspace, including but not limited to keys and access tokens, must be returned to the Hackerspace.}

\vspace{1.5\baselineskip}\section*{Organisation of General Meetings}
\addcontentsline{toc}{section}{Organisation of General Meetings}

@@

\vspace{1.5\baselineskip}\section*{Voting at General Meetings}
\addcontentsline{toc}{section}{Voting at General Meetings}

\subsection{General}
\subsubsection{A resolution put to the vote of a general meeting must be decided on a show of hands unless a poll is duly demanded in accordance with the Articles.}
\subsubsection[Only Members may vote at general meetings]{\textcolor{\fakecolour}{A person who is not a member of the Company shall not have any right to vote at a general meeting of the Company; but this is without prejudice to any right to vote on a resolution affecting the rights attached to a class of the Company's debentures.}} \label{subsubsection:nonmemberVoting}
\subsubsection[Proxies may vote on Members' behalf]{\fancyref{subsubsection:nonmemberVoting} shall not prevent a person who is a proxy for a member from voting at a general meeting of the Company.}

@@

\vspace{1.5\baselineskip}\section*{Written Resolutions}
\addcontentsline{toc}{section}{Written Resolutions}

@@

\newpage\section*{Administrative Arrangements and Miscellaneous}
\addcontentsline{toc}{section}{Administrative Arrangements and Miscellaneous}
